---
title: "GATT Project"
output: html_notebook
---
#LEGEND
COLUMNS (365 in total):
Year: year of trade

General Outline

Choose one of the 124 countries and conduct the research from that country’s perspective.

The general outline for the briefing will be:

Report on the state of the world economy and trade during ‘73-’79:
What’s the average yearly GDP and per-capita GDP for the countries listed?

```{r}
repcode<-table(gatt_cln$rep_code)
partcode<-table(gatt_cln$part_code)

#126 rep code countries
#124 part code countries

install.packages("data.table")
require(data.table)
setDT(gatt_cln)[, .(count = uniqueN(gdp_rep)), by = year]







```


install.packages("tidyverse")
require(tidyverse)

install.packages("dplyr")
require(dplyr)

Which year registered the sharpest increase in the overall trade (is it better by chance?)?
Repeat the analysis considering two subgroups: GATT vs non-GATT (or any other grouping of your choice)

```{r}
#lets sum the total trade per year

agg<-aggregate(gatt_cln$trade, by=list(year=gatt_cln$year), FUN=sum)
plot(agg,xlab="Year",ylab="Total Trade")

agg_gatt<-aggregate(gatt_cln$trade, by=list(year=gatt_cln$year,gatt_member=gatt_cln$gatt_defacto_rep), FUN=sum)
agg_gatt


```

```{r}
# Which year registered the sharpest increase in the overall trade (is it better by chance?)?
library(dplyr)
gatt_c <- gatt_cln[(gatt_cln$gatt_defacto_rep == 1) | (gatt_cln$gatt_dejure_rep == 1), ]
non_gatt_c <- gatt_cln[(gatt_cln$gatt_defacto_rep == 0) & (gatt_cln$gatt_dejure_rep == 0), ]
nrow(gatt_c)
nrow(gatt_c) + nrow(non_gatt_c)
yearly_trade_gatt <- gatt_c %>%
  group_by(year) %>%
  summarise(mean_trade = mean(trade, na.rm = TRUE))
yearly_trade_ngatt <- non_gatt_c %>%
  group_by(year) %>%
  summarise(mean_trade = mean(trade, na.rm = TRUE))
yearly_trade_gatt
yearly_trade_ngatt

  
```


Use resampling methods to increase the robustness of the results
Design and setup a regression model to justify:

Whether your country need to join/leave the GATT
Which commodity your investors should trade. (Which country and which commodity)
Expand or modify your analysis as you see fit, add more research questions and use statistical methods










